---
title: "VPT with Robots"
subtitle: 'Response-Time (RT) Analysis: Human model'

author: 
- Joel Currie^[University of Aberdeen, j.currie.22@abdn.ac.uk], Katrina Louise McDonough^[University of East Anglia], Agnieszka Wykowska^[Istituto Italiano di Tecnologia], Maria Elena Giannaccini^[University of Aberdeen], Patric Bach^[University of Aberdeen]


date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
eval = TRUE
knitr::opts_chunk$set(echo = FALSE)
rm(list = ls())
library(lme4)
library(sjPlot)
library(dplyr)
```


# Human Model:

```{r}
data <- read.csv("data_preprocessed.csv")

mod_human_centred <- lmer(RT ~ self_theta_centred * Exposure + other_theta_centred * Exposure + 
                   (1 + Exposure + self_theta_centred + other_theta_centred|subject) 
                 ,data=filter(data, correct == 1, Agent == 'Human'), control = lmerControl(optimizer = "bobyqa"))
```
## Effects of Interest:
### Self Theta:

```{r}
plot_model(mod_human_centred, type = "pred", terms = c("self_theta_centred"))
```

As can be seen above, RTs  show the expected linear increase as the disparity between self-perspective and stimulus orientation increases ($E = 415.7, CI = [370.1 - 461.2], p < .001$).

### Other Theta:

```{r}
plot_model(mod_human_centred, type = "pred", terms = c("other_theta_centred"))
```

Our Human-Human step-down model confirms the main effect of the Other-Perspective for the Human-Human group ($E = 39.2, CI = [16.4 - 62.1], p = .001$).

## Other Fixed effects and Interactions:
### Exposure:

```{r}
plot_model(mod_human_centred, type = "pred", terms = c("Exposure"))
```

Generally participants RTs got faster over the course of the experiment, as participants were exposed to more trials they became better at the task ($E = -135.9, CI = [-205.9 - -66.0], p < .001$).  

### Agent * Exposure* Other_theta:
```{r}
plot_model(mod_human_centred, type = "pred", terms = c("Exposure", "other_theta_centred"))
```

We found a small interaction in the in the Human group between other theta and Exposure ($E = 72.4, CI = [-139.7 - -5.0], p = .035$). This interaction *could* imply that as the experiment progresses participants rely less on their partners perspective, and the VPT effect appears to get weaker. This interaction was also found in our full model.

## Model Construciton:
```{r, echo=T, results='hide'}
mod_human_centred <- lmer(RT ~ self_theta_centred * Exposure + other_theta_centred * Exposure + 
                   (1 + Exposure + self_theta_centred + other_theta_centred|subject) 
                 ,data=filter(data, correct == 1, Agent == 'Human'), control = lmerControl(optimizer = "bobyqa"))
```

## Output of model:
```{r}
tab_model(mod_human_centred)
```





