---
title: "VPT with Pepper"
subtitle: 'Response-Time (RT) Analysis: Full model'

author: 
- Joel Currie^[University of Aberdeen, j.currie.22@abdn.ac.uk], Katrina Louise McDonough^[University of East Anglia], Agnieszka Wykowska^[Istituto Italiano di Tecnologia], Maria Elena Giannaccini^[University of Aberdeen], Patric Bach^[University of Aberdeen]


date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
eval = TRUE
knitr::opts_chunk$set(echo = FALSE)
rm(list = ls())
library(lme4)
library(sjPlot)
library(dplyr)
```


# Full Model:

```{r}
data <- read.csv("data_preprocessed.csv")

mod_full_cat_center2 <- lmer(RT ~ self_theta_centred * Agent_cat * Exposure + other_theta_centred * Agent_cat * Exposure + 
                              (1 + Exposure + self_theta_centred + other_theta_centred|subject) 
                            ,data=filter(data, correct == 1), control = lmerControl(optimizer = "bobyqa"))
```
## Effects of Interest:
### Self Theta:

```{r}
plot_model(mod_full_cat_center2, type = "pred", terms = c("self_theta_centred", "Agent_cat"))
```

As can be seen above, RTs  show the expected linear increase as the disparity between self-perspective and stimulus orientation increases ($E = 412.1, CI = [364.3 - 459.9], p < .001$).

### Other Theta:

```{r}
plot_model(mod_full_cat_center2, type = "pred", terms = c("other_theta_centred", "Agent_cat"))
```

Our full-model failed to identify the main effect of Other-Perspective ($E = -0.2, CI = [-21.4 - 21.0], p = .986$), however detected an interaction between Other-Perspective, and the Human agent category ($E = 39.5, CI = [9.3 - 69.8], p = .010$) signalling that the expected VPT effect was only present in the group where participants were paired with other human participants.

Though visually, there appears to be a systematic difference in RTs between the Animate Robot group and the Human/Inanimate Robot, this is not statistically significant. 

## Other Fixed effects and Interactions:
### Exposure:

```{r}
plot_model(mod_full_cat_center2, type = "pred", terms = c("Exposure"))
```
Generally participants RTs got faster over the course of the experiment, as participants were exposed to more trials they became better at the task ($E = -147.5, CI = [-204.0 - -91.0], p < .001$).  

### Agent * Exposure* Other_theta:
```{r}
plot_model(mod_full_cat_center2, type = "pred", terms = c("Exposure", "other_theta_centred", "Agent_cat"))
```

We found a small interaction in the between the Human group, other theta and Exposure ($E = -107.3, CI = [-200.5 - -14.1], p = .024$). This interaction *could* imply that as the experiment progresses participants rely less on their partners perspective, and the VPT effect appears to get weaker. 

## Model Construciton:
```{r, echo=T, results='hide'}
mod_full_cat_center2 <- lmer(RT ~ self_theta_centred * Agent_cat * Exposure + other_theta_centred * Agent_cat * Exposure + 
                              (1 + Exposure + self_theta_centred + other_theta_centred|subject) 
                            ,data=filter(data, correct == 1), control = lmerControl(optimizer = "bobyqa"))
```

## Output of model:
```{r}
tab_model(mod_full_cat_center2)
```





